---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
data(msleep)
library(infer)
```

H0: µ = 7  0.05
HA: µ != 7

reject null hypothesis, accept HA, meaning the mean sleep_total in the sampled 
population of animal types does differ from the typical value for jabberwockies.

```{r}
null_distribution <- msleep %>%
  specify(response = sleep_total) %>%
  hypothesize(null = "point", mu = 7) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "mean")

observed_stat <- msleep %>%
  specify(response = sleep_total) %>%
  calculate(stat = "mean")

null_distribution %>%
  visualise() +
  shade_p_value(direction = "both", obs_stat = observed_stat)

null_distribution %>%
  get_p_value(direction = "both", obs_stat = observed_stat)
```

```{r}
msleep %>%
distinct(vore)
```

H0: µomni - µherbi = 0
HA: µomni - µherbi > 0
```{r}
msleep %>%
  group_by(vore) %>%
  summarise(n = n())

msleep %>%
  ggplot() +
  aes(y = sleep_total, x = vore) +
  geom_boxplot()

null_distribution <- msleep %>%
  filter(vore %in% c("omni", "herbi")) %>%
  specify(sleep_total ~ vore) %>%
  hypothesise(null = "independence") %>%
  generate(reps = 5000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("herbi", "omni"))

observed_stat <- msleep %>%
  filter(vore %in% c("omni", "herbi")) %>%
  specify(sleep_total ~ vore) %>%
  calculate(stat = "diff in means", order = c("herbi", "omni"))

null_distribution %>%
  visualise() +
  shade_p_value(obs_stat = observed_stat, direction =  "left")

p_value <- null_distribution %>%
  get_p_value(obs_stat = observed_stat, direction = "left")

```
Fail to reject H0, no proven significant statistical difference.

H0: πdomesticated = 0.5
HA: πdomesticated > 0.5
```{r}

observed_stat <- msleep %>%
  group_by(conservation) %>%
  summarise(proportion = n()/nrow(msleep)) %>%
  filter(conservation == "domesticated")

msleep_domesticated <- msleep %>%
  mutate(domesticated = if_else(conservation == "domesticated",
                                "domesticated", "not domesticated"))

null_distribution <- msleep_domesticated %>%
  specify(response = domesticated, success = "domesticated") %>%
  hypothesise(null = "point", p = 0.5) %>%
  generate(reps = 5000, type = "simulate") %>%
  calculate(stat = "prop")

null_distribution %>%
  visualise(bins = 30) +
  shade_p_value(obs_stat = observed_stat, direction = "left")

null_distribution %>%
  get_p_value(obs_stat = observed_stat, direction = "left")
```
Reject H0, conclude there's a significant difference.

Question 1.
You work for a independent coffee shop. The boss tells you that she thinks that around 40% of people in the town (population 30,000) know of the coffee shop, but you are skeptical of the estimate. You conduct a random survey of 200 people in the town, asking if respondents are aware of your coffee shop. You want to use the sample to test the hypothesis that 40% or more of the town’s population have heard of the coffee shop.

test - One sample test for proportion
H0: πknow_shop = 0.4
HA: πknow_shop > 0.4
H0: 40% of people know the shop
HA: Greater than 40% of people know the shop
Method: simulation



Question 2.
You work for a website design company and have performed an A/B test on the position of a banner on a website promoting a particular item.

A/B testing A method comparing two versions of a web page, email, flyer or other marketing device against each other to determine which version performs better. As it is essentially a controlled experiment, the design should try to ensure that the groups experiencing both versions of the marketing device are equivalent and representative of the population.

You selected five days at random last month and then randomly selected 200 of each sampled day’s users into group A and another 200 of that day’s users into group B. Group A continued to be shown the banner at the right hand side of the webpage (its usual position) while group B was shown the banner at the top of the page. You monitored each sampled user’s interactions with the website, in particular the ‘click through rate’ (CTR) on the banner, i.e. what proportion of sampled users clicked on the banner. You want to use the sampled data to test the hypothesis that website users overall are more likely to click on the banner if positioned at the top of the page

test - Two sample test for mean
H0: µtop_banner = 0
HA: µtop_banner > 0
H0:less or equal folk click the top banner in comparison to the side banner
H1: More folk click the top banner
Method: Permutation

Question 3.
You work as an analyst for a car manufacturing company - they have specific standards they must meet for standards and regulation purposes. You have been asked to check the quality control of the manufacture of a particular car part. You have been given data on a sample of 200 parts produced over the period of a week (the sampled parts were pulled at random from the production line and measured: the factory produced a lot more than 200 parts that week). The specification of the part stipulates a width of 145mm, and the manufacturing process is said to have ‘drifted’ if the mean width of parts differs significantly from 145mm. You want to use the sampled measurements to test whether the process overall has drifted.

test - One sample mean test two sided.
H0: µdrifted = 145
HA: µdrifted != 145
H0: The overall process hasn't drifted significantly
H1: The overall process has drifted significantly
Method: Bootstrap


Question 1.

Coffee shop problem. Significance level: 0.05, calculated p-value: 0.07

We fail to reject our null hypothesis and therefore determine our bosses statement to be
inaccurate don't have enough evidence to prove the awareness is significantly greater
than 40.


Question 2.

Website company problem. Significance level: 0.01, p-value: 0.006

We reject H0, suggesting that there's a significantly greater amount of clicks 
when the banner's placed at the top of the page.


Question 3.

Manufacturing company problem. Significance level: 0.05, p-value: 0.55

We fail to reject H0, suggesting the process hasn't drifted 
significantly.